The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-18 article.tex
Cite paper using the CDK for reaction fingerprints (closes #32)

Open Source cheminformatics has made significant steps forward recently~\cite{OBoyle2011}.
The Chemistry Development Kit (CDK) is one of the tools under the Blue Obelisk wings,
and previously documented version have been widely adopted~\cite{Steinbeck2003,Steinbeck2006}.
For example, new tools expose CDK functionality in larger platforms such as Cinfony~\cite{OBoyle2008},
rcdk~\cite{Guha2007}, and plugins for Taverna~\cite{Truszkowski2011},
KNIME~\cite{Beisken2013}, ChemViz2 for Cytoscape~\cite{ChemViz2}, and LICSS for
Microsoft Excel~\cite{Lawson2012}.
Furthermore, projects with specific functionality have emerged building on the CDK, including
jCompoundMapper~\cite{Hinselmann2011}, ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012},
PaDEL~\cite{yap2011padel}, ReactPRED~\cite{ReactPRED}, SMSD~\cite{Rahman2009,Rahman2014,Rahman2016},
WhichCyp~\cite{Rostkowski2013}, MetaPrint2D~\cite{Carlsson2010}, and the IUPHAR/BPS Guide to Pharmacology database~\cite{Southan2016}.
Other tools used previous versions already, and follow
newer releases of the CDK, such as Bioclipse~\cite{spjuth2007bioclipse,
spjuth2009bioclipse} and AMBIT~\cite{jeliazkova2011ambit,jeliazkova2011ambitsmarts,kochev2013ambit}. While the above
tools suggest that the CDK is primarily used to create general tools, it is
important to note that it is also used to solve specific questions, like finding
the maximally bridging rings in chemical structures~\cite{Marth2015}.

>>>>

Open Source cheminformatics has made significant steps forward recently~\cite{OBoyle2011}.
The Chemistry Development Kit (CDK) is one of the tools under the Blue Obelisk wings,
and previously documented version have been widely adopted~\cite{Steinbeck2003,Steinbeck2006}.
For example, new tools expose CDK functionality in larger platforms such as Cinfony~\cite{OBoyle2008},
rcdk~\cite{Guha2007}, and plugins for Taverna~\cite{Truszkowski2011},
KNIME~\cite{Beisken2013}, ChemViz2 for Cytoscape~\cite{ChemViz2}, and LICSS for
Microsoft Excel~\cite{Lawson2012}.
Furthermore, projects with specific functionality have emerged building on the CDK, including
jCompoundMapper~\cite{Hinselmann2011}, ScaffoldHunter~\cite{wetzel2009interactive}, OMG~\cite{Peironcely2012},
PaDEL~\cite{yap2011padel}, ReactPRED~\cite{ReactPRED}, SMSD~\cite{Rahman2009,Rahman2014,Rahman2016},
WhichCyp~\cite{Rostkowski2013}, MetaPrint2D~\cite{Carlsson2010}, and the IUPHAR/BPS Guide to Pharmacology database~\cite{Southan2016}.
Other tools used previous versions already, and follow
newer releases of the CDK, such as Bioclipse~\cite{spjuth2007bioclipse,
spjuth2009bioclipse} and AMBIT~\cite{jeliazkova2011ambit,jeliazkova2011ambitsmarts,kochev2013ambit}. While the above
tools suggest that the CDK is primarily used to create general tools, it is
important to note that it is also used to solve specific questions, like finding
the maximally bridging rings in chemical structures~\cite{Marth2015}, and
defining fingerprints for organic reactions~\cite{Segler2016}.
